---
output: pdf_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../output") })
---

# Libraries

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(lubridate)
```

# Data Import

```{r}
week9_tbl <- read_csv("../data/week3.csv") %>%
              mutate(timeStart = ymd_hms(timeStart),
                     timeEnd = ymd_hms(timeEnd),
                     condition = factor(condition, 
                                        levels = c("A", "B", "C"), 
                                        labels = c("Block A", "Block B", "Control")),
                     gender = factor(gender, 
                                     levels = c("M", "F"), 
                                     labels = c("Male", "Female")),
                     mean1_5 = (q1 + q2 + q3 + q4 + q5)/5,
                     mean6_10 = (q6 + q7 + q8 + q9 + q10)/5)
```

- changed timeStart and timeEnd to POSIXct format 
- created factors for condition and gender
- calculated mean score on questions 1 - 5
- calculated mean score on questions 6 - 10

# Data Visualization

```{r, echo=FALSE}
p <- ggplot(week9_tbl, aes(x = mean1_5, y  = mean6_10)) +
      geom_point() +
      geom_smooth(method = "lm", se = FALSE)
p
```

The plot shows the relationship between the mean score on questions 1 through 5 and the mean score on questions 6 through 10 where each point represents an individual and the line is the OLS regression line. 

# Analysis

```{r}
r <- cor.test(week9_tbl$mean1_5, week9_tbl$mean6_10)
r
```

The correlation was `r round(r$estimate, 2)` (p=`r round(r$p.value, 2)`), which is not statistically significant.
